---
title: "background.rmd"
author: "Shane Connuck"
date: "2022-10-06"
output: html_document
---
```{r}
library(tidyverse)
```
Last time, I was trying to use the play-by-play data. That contained every single play from every NBA game from 2016 to 2021. I'm trying to find out about some games the Nets played during one season. So, I decided it wasn't the best dataframe to use.

Instead, let's take a look at the NBA player box scores. I'm going to specify that this is for the 2020-2021 season and not all five years.
```{r}
tictoc::tic()
progressr::with_progress({
  nba_player_box <- hoopR::load_nba_player_box(2020:2021)
})
tictoc::toc()
```
```{r}
glue::glue("{nrow(nba_player_box)} rows of NBA player boxscore data from {length(unique(nba_player_box$game_id))} games.")
```

```{r}
dplyr::glimpse(nba_player_box)
```
```{r}
nba_player_box %>% 
  filter(team_short_display_name == "Nets") %>% 
  group_by(athlete_display_name)
```
Ah, there are the guys.
```{r}
nba_player_box %>% 
  filter(team_short_display_name == "Nets") %>% 
  filter(athlete_display_name == "Kevin Durant") %>% 
  summarise(athlete_display_name, pts)
```
So, this is showing all of the points Kevin Durant scored during the 47 games he played.
```{r}
nba_player_box %>% 
  filter(team_short_display_name == "Nets") %>% 
  filter(athlete_display_name == "James Harden") %>% 
  summarise(athlete_display_name, pts)
```
Class five-point and scoreless performances from the now 76er.
```{r}
nba_player_box %>% 
  filter(team_short_display_name == "Nets") %>% 
  filter(athlete_display_name == "Kyrie Irving") %>% 
  summarise(athlete_display_name, pts)
```
Somehow, Kyrie played in the most games out of the three in that season.

So, what I'm trying to find here is the number of game box scores in which all three of those names showed up. Then, compare their scoring to the rest of the team.

However, these box scores are showing each individual player's statistic, while the team box scores I've loaded as well don't have any individual players mentioned.
```{r}
nba_player_box %>% 
  filter(team_short_display_name == "Nets") %>% 
  group_by(athlete_display_name == "Kevin Durant", athlete_display_name == "Kyrie Irving", athlete_display_name == "James Harden", active == "FALSE")
```
So, I'm seeing that I'm going to have to use the "active" column to determine which games those players suited up.